Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-08 paper.tex
discussion os

With an small investment in infrastructure and in maintenance can be fulfilled the requests of GPU-capable hosts in a completely transparent way for the user.
Energy can be saved, not only Thanks to the remote access and the ability to emulate several GPUs from a real one, but also  by grouping the accelerators in a single machine (when possible) or turning down nodes when their GPUs are not necessary.

>>>>

The requests of GPU-capable hosts in a completely transparent way for the user can be fulfilled with an small investment in infrastructure and in maintenance.
Energy can be saved, not only thanks to the remote access and the ability to emulate several GPUs from a real one, but also  by grouping the accelerators in a single machine (when possible) or turning down nodes when their GPUs are not necessary.
